Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-18 paper.tex
Change float priority
Rewording
Some work on introduction

Scaled physical models are often used in science and engineering to approximate
real-world systems. In the fields of wind and marine hydrokinetic (MHK) energy,
scaled physical models are used to validate numerical models, test prototypes of
individual devices, and design or investigate arrays of devices. Despite being
significantly less expensive, there is still some concern at which scale an
experiment must be performed to be relevant to full-scale application.

@@

When designing or studying arrays, it is very common to use very small
(geometrically) scaled devices. Sometimes these are not even models of turbines,
but wake generating objects, e.g., porous disks, that are meant to replicate the
wakes of real turbines. In this case, it is of interest to determine at what
scale one might be able to realistically study wake flows in an array, and also
to evaluate the effectiveness of a wake generator, i.e., a wake generator may do
a fine job simulating a scaled turbine, but how well can it simulate a real
turbine?

Previously, Bachant and Wosnik \cite{Bachant2015-JoT} showed that a cross-flow
turbine wake's unique mean flow field is responsible for accelerated wake
recovery when compared with conventional axial-flow propeller-type turbines.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/all_foils_re_dep}
\caption{Foil section characteristics computed by XFOIL for various $Re_c$.}
\label{fig:foil-Re-dep}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/foil_kinematics_ct}
\caption{Geometric angle of attack (a), relative velocity (b) and torque coefficient
(c) calculated with a NACA 0020 foil.}
\label{fig:blade-kinematics}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{figures/cft_re_dep_foils}
\caption{Reynolds number dependence of the peak torque coefficient calculated using 
only static foil coefficients and blade kinematics.}
\label{fig:foils-C_T-Re-dep}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/wake_spectra}
\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$, 
$y/R=-1.0$ (a) and $y/R=1.5$ (b). Dashed vertical
lines indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}
\label{fig:wake-spectra}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}
\caption{Momentum transport quantities.}
\label{fig:mom-bar-graph}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
\caption{Mean kinetic energy transport quantities.}
\label{fig:K-bar-graph}
\end{figure}

Totals for all the wake transport terms calculated are plotted in
Figure~\ref{fig:wake-trans-totals}. We see that in general wake transport is
enhanced at lower Reynolds numbers and levels off consistent with the power
coefficient data. This is an important consideration if studying sub-scale
models of turbine arrays, where increased levels of wake recovery will motivate
different ideal array configurations when compared with full-scale turbines.

\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{figures/wake_trans_totals}
\caption{Normalized transport totals from Figures~\ref{fig:mom-bar-graph} and 
\ref{fig:K-bar-graph} plotted versus Reynolds number.}
\label{fig:wake-trans-totals}
\end{figure}

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. In the fields of wind and marine hydrokinetic (MHK) energy,
scaled physical models are used to validate predictive numerical models, predict
full-scale performance of individual turbines, and design or investigate arrays
of devices. Despite being significantly less expensive, there is still some
concern at which scale an experiment must be performed to be relevant to
full-scale application.

@@

When designing or studying arrays, it is common to use very small
(geometrically) scaled devices. 
% %
\todo[inline]{Get a reference for this, and a sample geometric scale.} 
% %
Sometimes these are not even models of turbines, but
wake generating objects, e.g., porous disks, that are meant to replicate the
wakes of real turbines. In this case, it is of interest to determine at what
scale one might be able to realistically study wake flows in an array, and also
to evaluate the effectiveness of a wake generator. In other words, a wake
generator may do a fine job simulating a scaled turbine, but how well can it
simulate a real turbine?

Previously, Bachant and Wosnik \cite{Bachant2015-JoT} showed that a cross-flow
turbine wake's unique vortical mean flow field is responsible for accelerated
wake recovery when compared with conventional axial-flow propeller-type
turbines. In this study we seek to replicate the same energy balance
considerations at multiple Reynolds numbers, to examine the implications on how
small scale, i.e. low Reynolds number experiments may be used to study flows in
turbine arrays.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.95\textwidth]{figures/all_foils_re_dep}
\caption{Foil section characteristics computed by XFOIL for various $Re_c$.}
\label{fig:foil-Re-dep}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.95\textwidth]{figures/foil_kinematics_ct}
\caption{Geometric angle of attack (a), relative velocity (b) and torque coefficient
(c) calculated with a NACA 0020 foil.}
\label{fig:blade-kinematics}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\textwidth]{figures/cft_re_dep_foils}
\caption{Reynolds number dependence of the peak torque coefficient calculated using 
only static foil coefficients and blade kinematics.}
\label{fig:foils-C_T-Re-dep}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.95\textwidth]{figures/wake_spectra}
\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$, 
$y/R=-1.0$ (a) and $y/R=1.5$ (b). Dashed vertical
lines indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}
\label{fig:wake-spectra}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}
\caption{Momentum transport quantities.}
\label{fig:mom-bar-graph}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
\caption{Mean kinetic energy transport quantities.}
\label{fig:K-bar-graph}
\end{figure}

Totals for all the wake transport terms calculated are plotted in
Figure~\ref{fig:wake-trans-totals}. We see that in general wake transport is
enhanced at lower Reynolds numbers and levels off consistent with the behavior
of the  turbine power coefficient. This is an important consideration if
studying sub-scale models of turbine arrays, where increased levels of wake
recovery will motivate different ideal array configurations when compared with
full-scale turbines.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\textwidth]{figures/wake_trans_totals}
\caption{Normalized transport totals from Figures~\ref{fig:mom-bar-graph} and 
\ref{fig:K-bar-graph} plotted versus Reynolds number.}
\label{fig:wake-trans-totals}
\end{figure}
